SDGs

### 2023-02-20 Trilemma_clustering.Rmd
first paper draft + older files

```{r}
df_dat |> 
    arrange(desc(EFconsPerCap))
```

@@

```{r fig.width=7, fig.height=8}
df_summary |> 
    mutate(clus = stab@clusterObjs$kmeans$`3`$cluster ) |> 
    mutate(country = as_factor(country)) |> 
    mutate(country = fct_reorder2(country, magnitude_a, Gini)) |> 
    pivot_longer(
        cols = sd_magnitude:gamma_a, names_to = "vars", 
        values_to = "vals") |> 
    ggplot(aes(vals, country)) +
    geom_col(aes(fill = as.factor(clus))) +
    facet_grid(clus~vars, scales = "free") +
    theme_light(base_size = 10)
```

>>>>

```{r}
df_dat |> 
    arrange(desc(EFconsPerCap))

#save(df_dat, file = "data/cleaned_trilemma.RData")
```

@@

```{r fig.width=7, fig.height=8}
df_summary |> 
    mutate(clus = stab@clusterObjs$kmeans$`3`$cluster ) |> 
    mutate(country = as_factor(country)) |> 
    mutate(country = fct_reorder2(country, magnitude, Gini)) |> 
    pivot_longer(
        cols = sd_magnitude:gamma, names_to = "vars", 
        values_to = "vals") |> 
    ggplot(aes(vals, country)) +
    geom_col(aes(fill = as.factor(clus))) +
    facet_grid(clus~vars, scales = "free") +
    theme_light(base_size = 10)
```

### 2023-02-20 inequality-SDGs.Rmd
first paper draft + older files

@@

```{r}
dat |>
    filter(indicator_name %in% vars, country_code %in% complete_countries) |> 
    select(-x35) |> 
    pivot_longer(cols = x1990:last_col(), values_to = "value", names_to = "year") |> 
    mutate(year = str_remove(year, "x"), year = as.numeric(year)) |> 
    filter(year >= 2000, year < 2019) |>  # restricting time improves
    select(-indicator_code) |> 
    pivot_wider(values_from = value, names_from = indicator_name) |> 
    GGally::ggpairs(
        columns = 4:12 ,
    lower = list(continuous = GGally::wrap("points", alpha = 0.5, size = 0.5)),
    diag = list(continuous = GGally::wrap("densityDiag", alpha = 0.2))
    # upper = list(continuous = GGally::wrap("cor", size = 2))
    ) + theme_light(base_size = 6)
```
Interpolate missing values

@@

@@

```{r}
summary(pca1)
```

@@

```
```{r}
mfa1
```

@@

>>>>

# ggsave(
#     plot = p, filename = "WB_environment_SDGs_othervars.png", path = "figures/", device = "png",
#     width = 6, height = 4, dpi = 400, bg = "white"
# )
```

@@

```{r warnings=FALSE, message=FALSE}
dat |>
    filter(indicator_name %in% vars, country_code %in% complete_countries) |> 
    select(-x35) |> 
    pivot_longer(cols = x1990:last_col(), values_to = "value", names_to = "year") |> 
    mutate(year = str_remove(year, "x"), year = as.numeric(year)) |> 
    filter(year >= 2000, year < 2019) |>  # restricting time improves
    select(-indicator_code) |> 
    pivot_wider(values_from = value, names_from = indicator_name) |> 
    GGally::ggpairs(
        columns = 4:12 ,
    lower = list(continuous = GGally::wrap("points", alpha = 0.5, size = 0.5)),
    diag = list(continuous = GGally::wrap("densityDiag", alpha = 0.2))
    # upper = list(continuous = GGally::wrap("cor", size = 2))
    ) + theme_light(base_size = 6)
```
Interpolate missing values

@@

```{r}
#save(df_dat, df_un_reduced, file = "data/cleaned_sdg.RData")
```

@@

```{r}
# summary(pca1)
```

@@

```
```{r}
mfa1$group
```

```{r}
mfa1 |> summary()
```

```{r}
ggbiplot::ggbiplot(
    pca1,
    labels = df_dat$country_code |> unique(),
    circle = TRUE,
    varname.abbrev = TRUE)
```

@@

```{r}
pca3 <- df_dat |> 
    ungroup() |> 
    mutate(year = as_factor(year)) |> 
    split(~year) |>
    map(function(x) select(x, where(is.numeric))) |> 
    map(function(x) princomp(x, center = TRUE, scale. = TRUE))
```

```{r}
pca3 |> map(biplot)
```

## Paper outline

Title: Trade-offs between biosphere goals and inequality at the national scale

Introduction

- Previous studies proposed the hypothesis of the trilemma
- Do the trade-offs hold at national scale with SDG data?

Methods:

- SDG datasets at national scale collected by World Bank and United Nations
- Selection of variables
- Multiple Factor Analysis (PCA over time)
- Clustering

Results:

-
